%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This paper describes a search for dark matter (DM) in events containing an energetic narrow or wide jet and an imbalance of transverse momentum (\ETm) in a dataset 
of pp collisions provided by the Large Hadron Collider (LHC) at a centre-of-mass energy of 8 TeV. The data were collected using the Compact Muon Solenoid (CMS) 
detector and correspond to an integrated luminosity of 19.7\fbinv. 

The search is the first at CMS to target the hadronic decay modes of the vector bosons in the mono-V (V=W or Z boson) channels. A multivariate V-tagging technique is 
employed to identify the individually resolved decay products of moderately boosted vector bosons. The exploration of mono-V production at high boost 
utilises recently developed techniques designed to exploit information 
available in the sub-structure of jets. The events are categorised according to the nature of the jets in the event and the signal extraction is performed by 
considering the $\ETm$ distribution in each event category. These two features provide improved sensitivity compared to the previous CMS monojet analysis~\cite{monojet1}. 

The existence of dark matter is one of the most compelling sources of evidence for physics beyond the Standard Model (SM) with a number of astrophysical observations 
suggesting an abundance of a non-baryonic form of matter in the universe. In many theories which extend the SM, the production of DM particles in high-energy hadron-hadron 
collisions, such as those produced at the Large Hadron Collider (LHC) is realised via a mediator which couples to both the SM and the DM particles.  
The canonical ``monojet'' search provides a model-independent means of exploring DM production at the LHC~\cite{monojet1,monojet2} while 
related ``mono-V'' (V=W/Z) searches~\cite{monolep,monoZHbb,Aad:2014vka,Aad:2013oja} target the associated production of DM with SM vector bosons, 
which can be enhanced in theories with non-universal DM couplings~\cite{IVDM}.  The interpretation of results from these and other DM searches at 
the Large Hadron Collider (LHC) have generally utilized effective field theories (EFT) that assume heavy mediators and DM production via contact interactions~\cite{Fox:2011pm}.  
The results of this analysis are interpreted using the simplified DM models,~\cite{simplified1,Buchmueller:2013dya}, which span a broad range of 
mediator and DM particle properties in order to compare sensitivity to the direct detection experiments while retaining validity as a description of DM 
production across the entire kinematic region accessible at the LHC. 

Simplified models assume an additional particle, a fermionic dark matter candidate, and an additional interaction that forces the production of a dark matter. 
For generality, it is assumes that this additional interaction is mediated by a generic spin-0 or spin-1 particle. 
The interactions are characterised by four distinct Lagrangians, known as the simplified models, written for a dark matter particle $\chi$ as, 

\begin{align}
\label{eq:LS} 
\mathcal{L}_{\mathrm{scalar}}&\supset\, -\,\frac{1}{2}m_{\rm MED}^2 S^2 - g_{\rm DM}  S \, \bar{\chi}\chi
 - \sum_{q=b,t} g_{SM}^q S \, \bar{q}q  - m_{\rm DM} \bar{\chi}\chi \,,
 \\
 \label{eq:LP} 
\mathcal{L}_{\rm{pseudo-scalar}}&\supset\, -\,\frac{1}{2}m_{\rm MED}^2 P^2 - i g_{\rm DM}  P \, \bar{\chi} \gamma^5\chi
 -\sum_{q=b,t}  i g_{SM}^q  P \, \bar{q}  \gamma^5q  - m_{\rm DM} \bar{\chi}\chi\,,
 \\
 \label{eq:LV} 
\mathcal{L}_{\mathrm{vector}}&\supset \, \frac{1}{2}m_{\rm MED}^2 Z'_{\mu} Z'^{\mu} - g_{\rm DM}Z'_{\mu} \bar{\chi}\gamma^{\mu}\chi -\sum_q g_{SM}^q Z'_{\mu} \bar{q}\gamma^{\mu}q - m_{\rm DM} \bar{\chi}\chi\,,
 \\
 \label{eq:LA} 
\mathcal{L}_{\rm{axial}}&\supset\,  \frac{1}{2}m_{\rm MED}^2 Z''_{\mu} Z''^{\mu} - g_{\rm DM} Z''_{\mu} \bar{\chi}\gamma^{\mu}\gamma^5\chi -\sum_q g_{SM}^q Z''_{\mu} \bar{q}\gamma^{\mu}\gamma^5q - m_{\rm DM} \bar{\chi}\chi\,
\end{align}

assuming pure scalar,psuedo-scalar, axial-vector and vector mediated interactions denoted by $S,P,Z',Z''$ mediators respectively. 
The couplings $g_{DM}$ and $g_{SM}$ denote the coupling of the mediator to the dark matter particle and to standard model particles respectively. 
The choice of this split in the Lagrangian is to parallel the existing separation with direct detection, into spin-dependent and spin-independent. 
Here, spin-independent can refer to either vector or scalar mediated interactions between which which direct detection makes no distinction. 
Spin-dependent interactions instead refer to axial-vector mediated interactions. Pseudo-scalar interactions are velocity suppressed in direct detection and thus not expected to contribute~\cite{HaischXXX}. We present results under for all four mediators comparing collider experiements with the strongest non-collider contraint for each mediator.

%~\cite{Abercrombie:2015wmb}.

%The canonical ``monojet'' search strategy provides a model-independent means of exploring this scenario~\cite{monojet1,monojet2} while 
%related ``mono-V'' (V=W/Z) searches~\cite{monolep,monoZHbb} target the associated production of DM with SM vector bosons, 
%which can be enhanced in theories with non-universal DM couplings~\cite{IVDM}.  The interpretation of results from these and other DM searches at 
%the Large Hadron Collider (LHC) have generally utilized effective field theories (EFT) that assume heavy mediators and DM production via contact interactions~\cite{Fox:2011pm}.  

This paper is structured as follows; After a brief description of the CMS detector is presented in Section 2, Section 3 outlines details of the signal simulation 
used in the analysis. Section 4 provides a description of the physics object reconstruction and the event selection and categorisation and Section 5 describes the 
background modelling used for the signal extraction. The results of this analysis and interpretations of the results in the context of simplified models for DM 
production are presented in Section 6.

